### 2024-04-08 README.qmd
Add pkg basics

```{r}
library(tidyverse)
u = "https://www.westyorkshire.police.uk/sites/default/files/2024-01/operation_snap_oct-dec_2023_0.xlsx"
download_and_read = function(u) {
    tmp = tempfile(fileext = ".xlsx")
    download.file(u, tmp, mode = "wb")
    readxl::read_excel(tmp)
}
d = download_and_read(u)
names(d)
#  [1] "REPORTER TRANSPORT MODE" "OFFENDER VEHICLE MAKE"  
#  [3] "OFFENDER VEHICLE MODEL"  "OFFENDER VEHICLE COLOUR"
#  [5] "OFFENCE"                 "DISTRICT"               
#  [7] "DISPOSAL"                "DATE OF SUBMISSION"     
#  [9] "...9"                    "OFF LOCATION"  
d_locations = d |>
  dplyr::pull(`OFF LOCATION`) |>
  head(10) |>
  lapply(FUN = stplanr::geo_code)
# d_geocoded = d |>
#   tidygeocoder::geocode("OFF LOCATION")
d_locations[[1]]
matrix(d_locations[[1]], ncol = 2)
sf::st_point(matrix(d_locations[[1]], ncol = 2))
d_locations_lengths = sapply(d_locations, function(x) {
    length(x)
    })

>>>>

```{r}
#| echo: false
#| eval: false
# Package setup:
usethis::use_description()
usethis::use_package("sf")
usethis::use_package("stplanr")
usethis::use_package("ggplot2")
usethis::use_package("dplyr")
usethis::use_r("opsnap")
```

# Installation

Install the package from GitHub:

```{r}
remotes::install_github("ITSLeeds/opsnap")
```

```{r}
library(tidyverse)
u = "https://www.westyorkshire.police.uk/sites/default/files/2024-01/operation_snap_oct-dec_2023_0.xlsx"
d = opsnap:::download_and_read(u)
names(d)
#  [1] "REPORTER TRANSPORT MODE" "OFFENDER VEHICLE MAKE"  
#  [3] "OFFENDER VEHICLE MODEL"  "OFFENDER VEHICLE COLOUR"
#  [5] "OFFENCE"                 "DISTRICT"               
#  [7] "DISPOSAL"                "DATE OF SUBMISSION"     
#  [9] "...9"                    "OFF LOCATION"  
d_locations = d |>
  dplyr::pull(`OFF LOCATION`) |>
  head(10) |>
  lapply(FUN = stplanr::geo_code)
# d_geocoded = d |>
#   tidygeocoder::geocode("OFF LOCATION")
d_locations[[1]]
matrix(d_locations[[1]], ncol = 2)
sf::st_point(matrix(d_locations[[1]], ncol = 2))
d_locations_lengths = sapply(d_locations, function(x) {
    length(x)
    })
